Title Here

### 2014-12-04 wearables_survey.tex
Rough outline!

\author{
% 1st. author
\alignauthor
Linda N. Lee
       \affaddr{University of California Berkeley}\\
       \email{lnl@berkeley.edu}
% 2nd. author
\alignauthor
Serge Egelman
       \affaddr{University of California Berkeley}\\
       \affaddr{International Computer Science Institute}\\
       \email{serge@cs.berkeley.edu}
% 3rd. author
\alignauthor David Wagner
       \affaddr{University of California Berkeley}\\
       \email{daw@cs.berkeley.edu}
}

@@

\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms to
the formatting guidelines for ACM SIG Proceedings.
It complements the document \textit{Author's Guide to Preparing
ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

@@

@@

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography

%  and remember to run:
% latex bibtex latex latex
% to resolve all references

%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Appendix Title}

>>>>

\author{
% 1st. author
\alignauthor
Linda N. Lee\\
       \affaddr{UC Berkeley}\\
       \email{lnl@berkeley.edu}
% 2nd. author
\alignauthor
Serge Egelman\\
       \affaddr{UC Berkeley}\\
       \affaddr{ICSI}\\
       \email{serge@cs.berkeley.edu}
% 3rd. author
\alignauthor David Wagner\\
       \affaddr{UC Berkeley}\\
       \email{daw@cs.berkeley.edu}
}

@@

\begin{abstract}
Hello world.
\end{abstract}

% A category with the (minimum) three required fields
\category{look it up}{keyword1}{keyword2}{keyword3}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{term1} {term2} {term3}

@@

%%%%%%%%%%%%%%%%%%%
%%%         PAPER BODY         %%%
%%%%%%%%%%%%%%%%%%%

@@

\section{Related Work}
\subsection{Privacy for Wearables}
\subsection{Privacy for Smartphones}
\subsection{User Perception}
\subsection{User Attitude}

\section{Approach}
\section{Scope}
\section{Calibration}

\section{Methodology}
\subsection{Rationale}
\subsection{Design}
\subsubsection{Question Synthesis}
\subsubsection{Validation}
focus group here
\subsection{Deployment}
\subsection{Recruitment}

\section{Survey}
say numbers here
\subsection{Format}
\subsubsection{Cubetastic}
\subsubsection{Tech Rankings}
\subsubsection{Open-Ended Question}
\subsubsection{Additional Questions}
demographics and IUIPC

\section{Results}
takeaways
\subsection{How Upset}
\subsection{Tech Perceptions}
\subsection{Risk Perceptions}

\section{Discussion}
\subsection{Limitations}
\subsection{Future Research Directions}

\section{Conclusion}

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
NSF funding, SCRUB, BLUES. Also any people who helped.

%%%%%%%%%%%%%%%%%%%
%%%            BIB & ACKS          %%%
%%%%%%%%%%%%%%%%%%%

% The following two commands are all you need in the initial runs of your .tex file to produce the bib
%  and remember to run: latex bibtex latex latex to resolve all references

\bibliographystyle{abbrv}
\bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography

%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Full Survey}
\section{Detailed Situation Rankings}
\section{Detailed Tech Rankings}
\section{Focus Group Script}
